The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-08 paper/ms.tex
Add start of GC table

\usepackage{graphicx}
\usepackage{gensymb}
\usepackage{bm}
\usepackage{mathtools}

@@

\section{Coordinate System Offsets I. Measurement Errors} \label{sec:mes_err}
We consider the first potential source of coordinate system offsets which
would generate the action errors described in Section~\ref{sec:ref_frame}:
uncertainties in measurements of the position and velocity of the Sun relative
to the Galactic center. Converting from heliocentric to Galactocentric
coordinates relies on these measurements. Therefore, errors in their values
will induce a systematic offset in the Galactocentric phase-space position of
any observed star.

>>>>

\usepackage{graphicx}
\usepackage{gensymb}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{makecell}

@@

\section{Coordinate System Offsets I. Measurement Errors} \label{sec:mes_err}

\begin{deluxetable*}{cccccccccc}
\tablecaption{The highest-precision measurement of the parameters that define the Galactocentric coordinate system, and the error in each action that results for the thin-disk and thick-disk orbits we considered.
\label{tab:orbits}}
\tablehead{\colhead{name} & \colhead{description} & \colhead{value} & \colhead{uncertainty}
& \multicolumn{3}{c}{thin-disk orbit} & \multicolumn{3}{c}{thick-disk orbit} \\
 \colhead{ } & \colhead{ } & \colhead{ } & \colhead{ } & \colhead{$J_R$} & \colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$J_R$} & \colhead{$J_{\phi}$} & \colhead{$J_z$} }
\startdata 
$R_0$ & \makecell{distance to \\ Galactic center} & $8.178\,\kpc$ & $0.035\,\kpc$ ($0.3\%$) & $5.4\%$ & $0.3\%$ & \nodata & $5.9\%$ & $0.3\%$ & \nodata \\
$z_{\odot}$ & \makecell{solar height \\ above midplane} & $20.8\,\pc$ & $0.3\,\pc$ ($1.4\%$) & \nodata & \nodata & $0.5\%$ & \nodata & \nodata & $0.04\%$
\enddata
\end{deluxetable*}

We consider the first potential source of coordinate system offsets which
would generate the action errors described in Section~\ref{sec:ref_frame}:
uncertainties in measurements of the position and velocity of the Sun relative
to the Galactic center. Converting from heliocentric to Galactocentric
coordinates relies on these measurements. Therefore, errors in their values
will induce a systematic offset in the Galactocentric phase-space position of
any observed star.
